An exact method for the multi-product p-batch processing time maximization problem

### 2023-10-16 manuscript/manuscript.tex
updating paper - Improving the introduction

It is importante to note that some production units are capable of processing multiple jobs at the same time. In such a case batches of different products and sizes can be grouped and processed by these units as a single batch. It is therefore necessary to determine the set of "batches" that each new grouped batch will contain. The multi-product balancing problem consists of determining these groupings, seeking to minimize the overall makespan. \cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.  \cite{FowlerMonch2022} present a taxonomy and an extensive literature review for the p-batch problems. According to the authors, a p-batch problem can be classified as compatible setting - where there is no restriction on which jobs can be used to form a batch - and incompatible family case - where only jobs belonging to the same family can be used to form a batch. Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product \emph{s-batch} problem involving incompatible families with different job sizes and capacity constraints.

In a real production environment, some of these problems arise in a connected way, so many cientific works adress mixed multi-product batch problems. As example, \cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.

@@

\begin{enumerate}[label=\arabic*)]
\item \textbf{number of stages ($\sigma$)}: single stage (SS) or multistage (MS);
\item \textbf{layout($\lambda$)}: single unit (SU), flowshop (Fl), parallel (Pl), or networked (Nt) (convergent (CNt) and /or divergent (DNt));
\item \textbf{production mode ($\mu$)}: single-product campaing (SPC), mixed-product campaign (MPC), serial batching (s-batch) and/or parallel batching (p-batch);
\item \textbf{problem:($\pi$)}  : design (D), planning (P), sizing (Sz), scheduling (Sc) and/or balancing (B); 
\item \textbf{time horizon ($\eta$)}: single period (SP) or multiperiod (MP), cyclic (Cc);
\item \textbf{scenario ($\gamma$)}: static (St) or dynamic (Dn);
\item \textbf{input ($\iota$)}: deterministic (Dt) and/or stochastic (St);
\item \textbf{performance measure ($\delta$)}: capital cost (C), setup cost (SC), holding cost (HC), work-in-process cost (WIPC), net profit (NP), makespan (C$_{\textrm{max}}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$) and/or weighted $E/T$ ($wE/T$);
\item \textbf{others ($\rho$)}: capacited (UC), storage capacity (SC), work-in-process storage (WIP), due dates (DD), incompatible jobs (IJ). $\textrm{Z}$ 
\end{enumerate}

@@

\begin{table}[thb]
\begin{center}
\begin{small}
\begin{tabular}[c]{l l l}
reference & problem & contributions  \\
\cline {1-3} \\
\cite{Eilon1985} & $SS|SU|s\textrm{-}batch|Sc|SP$ &  analysis of the effect\\
& $St|Dt|SC, HC|-$  & of splitting batches \\
\cline {1-3} \\
Ravemark and & $MS|Pl|SPC|D|Cc|$ & convex mixed-integer\\
Rippin (1998) & $St|Dt|C|WIP$ & linear programming \\
& & model solved with \\
& & DICOPT++ \\
\cline {1-3} \\
Petkov and & $MS|Pl|SPC|D|Cc|$ & exact method\\
Maranas (1998)  & $St|St|NP|-$ & \\
\cline {1-3} \\
\cite{HeHui2008} & $SS|Pl|MPC|Sc|SP|$ & rule-based genetic \\
& $St|Dt|C_{\textrm{max}}, TT|UC, DD$ & algorithm \\
\cline {1-3} \\
\cite{FumeroEtAl2016} & $MS|Pl|MPC|D,P,Sc|Cc|$ & mixed-integer linear  \\
& $St|Dt|NP|UC,SC$ & programming model \\
& & solved with CPLEX \\
\cline {1-3} \\
\cite{LiuEtAl2020} & $MS|DNt|s\textrm{-}batch|Sz|MP$ & mixed-integer quadratic \\
& $|St|Dt|SC,WIPC|UC,WIP$ & programming model  \\
& & and exact algorithm \\
\cline {1-3} \\
\end{tabular}
\caption{Some contributions on the multi-product batch problems}
\label{tab:review}
\end{small}
\end{center}
\end{table}

@@

When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness. We named this problem multi-product p-batch processing time maximization (MBPTM) problem.

>>>>

It is importante to note that some production units are capable of processing multiple jobs at the same time. In such a case batches of different products and sizes can be grouped and processed by these units as a single batch. It is therefore necessary to determine the set of "batches" that each new grouped batch will contain. The multi-product balancing problem consists of determining these groupings, seeking to minimize the overall makespan. \cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.  \cite{FowlerMonch2022} present a taxonomy and an extensive literature review for the p-batch problems. According to the authors, a p-batch problem can be classified as compatible setting - where there is no restriction on which jobs can be used to form a batch - and incompatible family case - where only jobs belonging to the same family can be used to form a batch. Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product p-batch problem involving identical parallel units, capacity constraints, and incompatible families with different job sizes.

In a real production environment, some of these problems arise in a connected way, so many cientific works adress mixed multi-product batch problems. As example, \cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions. Also, de work of \cite{MendezEtAll2000}, previously mentioned, considers planning as an integrated part of solution in real-world multi-product batch plant scheduling and therefore includes the product batching problem in its proposed MILP continuous-time models and two-step systematic methodology.

@@

\begin{enumerate}[label=\arabic*)]
\item \textbf{number of stages ($\sigma$)}: single stage (SS) or multistage (MS);
\item \textbf{layout($\lambda$)}: single unit (SU), flowshop (Fl), parallel (Pl), or networked (Nt) (convergent (CNt) and /or divergent (DNt));
\item \textbf{production mode ($\mu$)}: single-product campaing (SPC), mixed-product campaign (MPC), serial batching (s-batch) and/or parallel batching (p-batch);
\item \textbf{problem:($\pi$)}  : design (D), planning (P), sizing (Sz), scheduling (Sc) and/or balancing (B); 
\item \textbf{time horizon ($\eta$)}: single period (SP) or multiperiod (MP), cyclic (Cc);
\item \textbf{scenario ($\gamma$)}: static (St) or dynamic (Dn);
\item \textbf{input ($\iota$)}: deterministic (Dt) and/or stochastic (St);
\item \textbf{performance measure ($\delta$)}: capital cost (C), setup cost (SC), holding cost (HC), work-in-process cost (WIPC), net profit (NP), makespan (C$_{\textrm{max}}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and processing time (PT);
\item \textbf{others ($\rho$)}: limited capacity units (LCU), storage capacity by product (PSC), storage capacity (SC), work-in-process storage (WIP), release time (RT), due dates (DD), incompatible families (IF), different processing rates (DPR).
\end{enumerate}

@@

\begin{table}[h!]
\begin{center}
\begin{small}
\begin{tabular}[c]{l l l}
reference & problem & contributions  \\
\cline {1-3} \\
\cite{Eilon1985} & $SS|SU|s\textrm{-}batch|Sc|SP$ &  analysis of the effect\\
& $St|Dt|SC, HC|-$  & of splitting batches \\
\cline {1-3} \\
Ravemark and & $MS|Pl|SPC|D|Cc|$ & convex mixed-integer\\
Rippin (1998) & $St|Dt|C|WIP$ & linear programming \\
& & model solved with \\
& & DICOPT++ \\
\cline {1-3} \\
Petkov and & $MS|Pl|SPC|D|Cc|$ & exact method\\
Maranas (1998)  & $St|St|NP|-$ & \\
\cline {1-3} \\
\cite{MendezEtAll2000} & $SS|\lambda|p,s\textrm{-}batch|P,Sc|\eta|\gamma|$ & two-step systematic \\
& $Dt|WIPC|RT, DD$& methodology \\
\cline {1-3} \\
\cite{HeHui2008} & $SS|Pl|MPC|Sc|SP|$ & rule-based genetic \\
& $St|Dt|C_{max}, TT|LCU, DD$ & algorithm \\
\cline {1-3} \\
\cite{FumeroEtAl2016} & $MS|Pl|MPC|D,P,Sc|Cc|$ & mixed-integer linear  \\
& $St|Dt|NP|LCU,USC$ & programming model \\
& & solved with CPLEX \\
\cline {1-3} \\
\cite{LiuEtAl2020} & $MS|DNt|s\textrm{-}batch|Sz|MP|St|$ & mixed-integer quadratic \\
& $Dt|SC,WIPC|LCU,WIP$ & programming model  \\
& & and exact algorithm \\
\cline {1-3} \\
\cite{LiEtAl2022} & $SS|Pl|p\textrm{-}batch|Sc,B|SP|$ & mixed-
integer linear \\
& $St|Dt|C_{max}|LCU, RT, IF$ & programming and \\
 & & a constraint-guided \\
 & & artificial immune \\
 & & system based algorithm \\ 
\cline {1-3} \\
\end{tabular}
\caption{Some contributions on the multi-product batch problems}
\label{tab:review}
\end{small}
\end{center}
\end{table}

@@

When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness. This problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ batch problem. For simplification purposes, we named this problem multi-product p-batch processing time maximization (MBPTM) problem.
